Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-07-23 text/manuscript-full-KS.qmd
add cover page

---
title: "Structuring College Access: The Market Segment Model and College Board Geomarkets"
author: ["Ozan Jaquette (UCLA)", "Karina Salazar (University of Arizona)", "Crystal Han (Stanford University)"]
bibliography: ./../assets/bib/cb_geomarket_bib.bib
csl: ./../assets/bib/chicago-author-date.csl
format:
  #docx:
  pdf:
    documentclass: article
    #papersize: letter
    number-sections: true
    number-depth: 2
    #toc: FALSE
    #pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    #keep_tex: true
    extensions: [andrewheiss/wordcount]
editor: visual
geometry:
  margin=1in
fontsize: 11pt
header-includes:
  - \usepackage{setspace}
  - \doublespacing
---

>>>>

---
title: "Structuring College Access: The Market Segment Model and College Board Geomarkets"
# author: ["Ozan Jaquette (UCLA)", "Karina Salazar (University of Arizona)", "Crystal Han (Stanford University)"]
bibliography: ./../assets/bib/cb_geomarket_bib.bib
csl: ./../assets/bib/chicago-author-date.csl
format:
  #docx:
  pdf:
    documentclass: article
    #papersize: letter
    number-sections: true
    number-depth: 2
    #toc: FALSE
    #pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    #keep_tex: true
    extensions: [andrewheiss/wordcount]
editor: visual
geometry:
  margin=1in
fontsize: 11pt
header-includes:
  - \usepackage{setspace}
  - \doublespacing
---
